---
title: "R Notebook"
output: html_notebook
---

```{r library, eval=TRUE, echo=FALSE}
library(dplyr)
library(tibble)
library(tidyr)
library(magrittr)
library(ggplot2)
library(reshape2)
library(tm)
library(base)
library(stringr)
library(RColorBrewer)
library(purrr)
library(stringr)
library(ggpubr)
library(leaflet)
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)


require(gdata)
```

```{r sick_score, eval=TRUE, echo=TRUE}
df = read.xls(("sick_score_xls.xls"), sheet = 1, header = TRUE)
sick_score <- rename(df)
sick_score <- data.frame(sick_score, stringsAsFactors = FALSE)
#abbreviate the Race to AA, C, LA, ME, AZN, AIAN, O
levels(sick_score$Race)[levels(sick_score$Race)=="A Indian/Alaskan Native"] <- "AIAN"
levels(sick_score$Race)[levels(sick_score$Race)=="African American"] <- "AA"
levels(sick_score$Race)[levels(sick_score$Race)=="Asian"] <- "AZN"
levels(sick_score$Race)[levels(sick_score$Race)=="Caucasian"] <- "C"
levels(sick_score$Race)[levels(sick_score$Race)=="latin American"] <- "LA"  #I repeated this for latin and Latin
levels(sick_score$Race)[levels(sick_score$Race)=="Middle Eastern"] <- "ME"
levels(sick_score$Race)[levels(sick_score$Race)=="Other"] <- "O"
```

```{r sick_score_map , eval=TRUE, echo=FALSE}
usa <- map_data("usa") # we already did this, but we can do it again
ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group = group)) +
  coord_fixed(1.5)

states <- map_data("state")

ggplot(data = states) +
  geom_polygon(aes(x = long, y = lat, fill = region, group = group), color = "white") +
  coord_fixed(1.3) +
  guides(fill=FALSE)


michigan <- subset(states, region %in% c("michigan","illinois", "ohio", "indiana"))
ggplot(data = michigan) +
  geom_polygon(aes(x = long, y = lat, group=group), fill = "palegreen", color = "black") + coord_fixed(1.3)

#zoom in on michigan
mi_df <- subset(states, region == "michigan")
head(mi_df)
counties <- map_data("county")
mi_county <- subset(counties, region == "michigan")
head(mi_county)

mi_base <- ggplot(data = mi_df, mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "gray") +
  geom_polygon(data = mi_county, fill = NA, color = "white") +
  geom_polygon(color = "black", fill = NA)


mi_base + theme_nothing()

mi_base + theme_nothing() +
  geom_polygon(data = mi_county, fill = NA, color = "white") +
  geom_polygon(color = "black", fill = NA)  # get the state border back on top


ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
)
group <- sick_score_geo %>% select(City, long, lat) %>% mutate(group = as.integer(factor(City))) %>%
   select(-City, -long, -lat)

mi_map <- mi_base +  ditch_the_axes + geom_polygon(color = "black", fill = NA) + theme_bw() +
  geom_polygon(data = subset_sick_score, aes( fill = City), color = "white", show.legend = FALSE)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

